What can GitHub and Googlecode Issues tell us about Exceptions in Android?

### 2014-08-24 android-stacks.tex
changing the focus. More inprovements in sec 2

>>>>

Android is an open source platform for mobile devices based on Linux kernel.
The plaftom is also comprised of a core Java library, a set of libraries third-party libraries e.g.  SQLite,
the Dalvik runtime environment, and the Aplication Framework which provides higher-level services to the applications
running on the platform e.g., controlling activities or providing data access.

Android supports an event-driven development model. The main element responsible for 
receiving the GUI events is called Activity, which is the unity of user interaction and execution in
Android. Android also provides APIs for data storage, communication between Activities, 
and other services. Moreover, it also provides frameworks for concurrent developement (e.g. AsyncTask) 
which is highly needed due to the demand of responsiveness in such environment  - 
mobile apps can easily become unresponsivedue to resurce limitation and excessive
 network access [shimidit and arie].
